--- 
title: "Mesa Statistics" 
author: "Akhil Bellamkonda" 
format: html 
execute:    
   echo: false 
---  
```{r}
#| label: setup 
#| message: false 
library(tidyverse) 
library(brms) 
library(tidybayes)
mesa_data <- read_csv('/Users/chittibellamkonda/Downloads/az_mesa_2023_01_26.csv')
```

```{r}
#| label: model 
#| cache: true 
df1 <- mesa_data |>    select(subject_sex, date, arrest_made)  
brm1 <- brm(data = df1,     formula = arrest_made ~ subject_sex + date, family = bernoulli(),     silent = 2,     refresh = 0,     seed = 13)

```
The rate of arrests in Mesa, Arizona, varies significantly based on the subject's sex. We used data from the Stanford Open Policing Project, specifically the Mesa dataset, which includes information on police stops conducted by the Mesa Police Department. The dataset provides records from January 1, 2011, to December 31, 2017, detailing variables like the subject's sex, the date of the stop, and whether an arrest was made. We employed a Bayesian regression model where the outcome variable is whether an arrest was made, modeled as a categorical response influenced by the subject's sex and the date of the police stop. This model allows us to quantify the relationship between gender and arrest probability while accounting for temporal patterns. Our analysis shows that males are statistically more likely to be arrested than females, with a predicted arrest probability that is 15% higher on average.



